Java Based Memory Latency Simulator

### 2020-11-21 finalPaper/paper.tex
Updated final paper and ref

\subsection{Java}
The simulator is written in Java, and therefore, you will need to have
Java installed to run it. See \url{https://www.java.com/en/download/}
 for more.

\subsection{Acquiring Source Code}
To download the simulator code, go to \url{osfinal.dachenhausen.org}
or \url{https://github.com/adamdachenhausen/cs330FinalProject} and clone the repository.
See \url{https:docs.github.com/en/free-pro-team@latest/github/
creating-cloning-and-archiving-repositories/cloning-a-repository} for more.

>>>>

\subsection{Java}
The simulator is written in Java, and therefore, you will need to have
Java installed to run it. See \href{https://www.java.com/en/download/}
 for more.

\subsection{Acquiring Source Code}
To download the simulator code, go to \href{osfinal.dachenhausen.org}
or \href{https://github.com/adamdachenhausen/cs330FinalProject} and clone the repository.
See
\href{https:docs.github.com/en/free-pro-team@latest/github/creating-cloning-and-archiving-repositories/cloning-a-repository}
for more.
